### 2014-03-08 src/analysis.Rnw
update

% ----------------------------------------------------------------------
<<one>>=
stats.one <- subset(stats.rest, grepl('^o[.]', operator))

o.stats.sel.one <- subset(o.f(stats.one), select=sel.colnames)
r.stats.sel.one <- subset(r.f(stats.one), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
colnames(o.stats.sel.one) <- new.colnames
colnames(r.stats.sel.one) <- new.colnames
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.one, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.one, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The one per element selection criteria results.}
\end{table*}

% ----------------------------------------------------------------------

\if 0
% START HERE
\begin{figure*}[t]
<<xx.per.sel,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
names=odata$s.power
x = (1:nrow(odata))
o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Project: Mutant Reduction vs Power',col='blue',pch=16)
axis(1, at=x, labels=names)
arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Project: Mutant Reduction vs Power',col='red',pch=16)
arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
@
\label{fig:sel}
\end{figure*}[t]

<<>>=
odata <- subset(stats.df, s.element=='class' & strategy=='xpercentperunit' & kind=='original')
rdata <- subset(stats.df, s.element=='class' & strategy=='xpercentperunit' & kind=='randoop')
odata$s.power
odata$mutant.reduction
@
\subsubsection{x\% selection}
\begin{figure*}[t]
<<x.per.sel.class,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
names=odata$s.power
x = (1:nrow(odata))
o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Class: Mutant Reduction vs Power',col='blue',pch=16)
axis(1, at=x, labels=names)
arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Class: Mutant Reduction vs Power',col='red',pch=16)
arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
@
\label{fig:sel}
\end{figure*}[t]

<<>>=
odata <- subset(stats.df, s.element=='method' & strategy=='xpercentperunit' & kind=='original')
rdata <- subset(stats.df, s.element=='method' & strategy=='xpercentperunit' & kind=='randoop')
odata$s.power
odata$mutant.reduction
@
\subsubsection{x\% selection}
\begin{figure*}[t]
<<x.per.sel.method,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
names=odata$s.power
x = (1:nrow(odata))
o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,400), xlab='Power',ylab='Reduction', main='Method: Mutant Reduction vs Power',col='blue',pch=16)
axis(1, at=x, labels=names)
arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,400), xlab='Power',ylab='Reduction', main='Method: Mutant Reduction vs Power',col='red',pch=16)
arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
@
\label{fig:sel}
\end{figure*}[t]

<<>>=
odata <- subset(stats.df, s.element=='line' & strategy=='xpercentperunit' & kind=='original')
rdata <- subset(stats.df, s.element=='line' & strategy=='xpercentperunit' & kind=='randoop')
odata$s.power
odata$mutant.reduction
@
\subsubsection{x\% selection}
\begin{figure*}[t]
<<x.per.sel.line,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
names=odata$s.power
x = (1:nrow(odata))
o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,20000), xlab='Power',ylab='Reduction', main='Line: Mutant Reduction vs Power',col='blue',pch=16)
axis(1, at=x, labels=names)
arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,20000), xlab='Power',ylab='Reduction', main='Line: Mutant Reduction vs Power',col='red',pch=16)
arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
@
\label{fig:sel}
\end{figure*}[t]

<<>>=
odata <- subset(stats.df, s.element=='line' & strategy=='xpercentperunit' & kind=='original')
rdata <- subset(stats.df, s.element=='line' & strategy=='xpercentperunit' & kind=='randoop')
odata$s.power
odata$mutant.reduction
@
\subsubsection{x\% selection}
\begin{figure*}[t]
<<x.per.sel.line.2,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
names=odata$s.power
x = (1:nrow(odata))
o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Line: Mutant Reduction vs Power',col='blue',pch=16)
axis(1, at=x, labels=names)
arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Line: Mutant Reduction vs Power',col='red',pch=16)
arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
@
\label{fig:sel}
\end{figure*}[t]

<<>>=
odata <- subset(stats.df, s.element=='class' & strategy=='xceilperunit' & kind=='original')
rdata <- subset(stats.df, s.element=='class' & strategy=='xceilperunit' & kind=='randoop')
@
\subsubsection{x\% selection}
\begin{figure*}[t]
<<x.per.sel.class.3,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
names=odata$s.power
x = (1:nrow(odata))
o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Ceil:Class: Mutant Reduction vs Power',col='blue',pch=16)
axis(1, at=x, labels=names)
arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Ceil:Class: Mutant Reduction vs Power',col='red',pch=16)
arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
@
\label{fig:sel}
\end{figure*}[t]

<<>>=
odata <- subset(stats.df, s.element=='line' & strategy=='xceilperunit' & kind=='original')
rdata <- subset(stats.df, s.element=='line' & strategy=='xceilperunit' & kind=='randoop')
@
\subsubsection{x\% selection}
\begin{figure*}[t]
<<x.per.sel.line.3,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
names=odata$s.power
x = (1:nrow(odata))
o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Ceil:Line: Mutant Reduction vs Power',col='blue',pch=16)
axis(1, at=x, labels=names)
arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Ceil:Line: Mutant Reduction vs Power',col='red',pch=16)
arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
@
\label{fig:sel}
\end{figure*}[t]

<<>>=
odata <- subset(stats.df, s.element=='project' & strategy=='xprobperunit' & kind=='original')
rdata <- subset(stats.df, s.element=='project' & strategy=='xprobperunit' & kind=='randoop')
@
\subsubsection{x\% selection}
\begin{figure*}[t]
<<x.per.sel.line.4,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
names=odata$s.power
x = c(2:6)
o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Prob:Project: Mutant Reduction vs Power',col='blue',pch=16)
axis(1, at=x, labels=names)
arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Prob:Project: Mutant Reduction vs Power',col='red',pch=16)
arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
@
\label{fig:sel}
\end{figure*}[t]

\subsection{SDL vs Random selection}
\begin{figure*}[t]
<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(mfrow=c(2,2))
with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
@
\label{fig:sdl1}
\caption{Statement Deletion vs One per line.}
\end{figure*}
<<results='asis'>>=
oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))

@@

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
o <- subset(oprand.x, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
r <- subset(oprand.x, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
o <- subset(oprand.l, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE,size='\\small')
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
r <- subset(oprand.l, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}

<<results='asis'>>=
opsel <- subset(stats.df,grepl('^..op', rownames(stats.df)))

o <- subset(opsel, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
print(xtable(o.x, caption='Original', label='table:selo'), include.rownames=FALSE, floating=FALSE,size='\\small')
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}

<<results='asis'>>=
r <- subset(opsel, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
print(xtable(r.x, caption='Randoop', label='table:selr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\end{table*}

>>>>

% ----------------------------------------------------------------------
\subsubsection{One per element}
The aim of this criteria is is to take the previous idea to the extreme. We choose only a single mutant per program element.

<<one>>=
stats.one <- subset(stats.rest, grepl('^o[.]', operator))

o.stats.sel.one <- subset(o.f(stats.one), select=sel.colnames)
r.stats.sel.one <- subset(r.f(stats.one), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
colnames(o.stats.sel.one) <- new.colnames
colnames(r.stats.sel.one) <- new.colnames
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.one, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.one, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The one per element selection criteria results.}
\label{tbl:onesel}
\end{table*}

\begin{figure*}[t]
<<one.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
ggplot(subset(o.one, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
\label{fig:onesel}
\end{figure*}

The values are given in Table~\ref{tbl:onesel}, and its visaulization is in Figure~\ref{fig:onesel}.
% ----------------------------------------------------------------------

% IGNORED FROM HERE.
\if 0
\subsection{SDL vs Random selection}
\begin{figure*}[t]
<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(mfrow=c(2,2))
with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
@
\label{fig:sdl1}
\caption{Statement Deletion vs One per line.}
\end{figure*}
<<results='asis'>>=
oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))

@@
